---
title: "Blue communities"
output: 
  html_document:
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(readxl)
library(janitor)
library(formattable)
```

```{r eval = TRUE, echo=FALSE}
original_xls <- "data/DATA EXTRACTION FINAL (15).xlsx"
de <- read_excel(original_xls, sheet = "Summary DE", .name_repair = "minimal")
Table_1_xls <- "data/DATA EXTRACTION FINAL (15).xlsx"
t1 <- read_excel(Table_1_xls, sheet = "Summary DE", .name_repair = "minimal")
```

### Biosphere reserve

Count frequency in raw data
```{r}
table(de$`Biosphere reserve`, useNA = 'always')
```

Remove NA, tidy names, calculate proportions
```{r eval = TRUE, echo = TRUE}
thisData <- de %>% 
  select('Biosphere reserve') %>% 
  drop_na()

names(thisData) <- 'Biosphere_reserve'
thisData[thisData == 'Komodo MPA',] <- 'Komodo'
thisData[thisData == 'Cat Tien (Dong Nai)',] <- 'Cat Tien'

thisTable <- tabyl(thisData$Biosphere_reserve)
names(thisTable)[1] <- 'Biosphere_reserve'
#names(thisTable)[3] <- 'proportion'

thisTable <- thisTable[order(-thisTable$n),]
rownames(thisTable) <- c()
formattable(thisTable, align='l')
```

### Data source

Count frequency in raw data
```{r}
table(de$`Data source`, useNA = 'always')
```

Remove NA, tidy names, calculate proportions
```{r eval = TRUE, echo = TRUE}
thisData <- de %>% 
  select('Data source') %>% 
  drop_na()

names(thisData) <- 'Data_source'
thisData[thisData == 'Conference abstract',] <- 'Conf. Abstract'
thisData[thisData == 'Peer-reviewed published literature',] <- 'Peer-reviewed'

thisTable <- tabyl(thisData$Data_source)
names(thisTable)[1] <- 'Data source'
#names(thisTable)[3] <- 'proportion'

thisTable <- thisTable[order(-thisTable$n),]
rownames(thisTable) <- c()
formattable(thisTable, align='l')
```

### Country

Count frequency in raw data
```{r}
table(de$Country, useNA = 'always')
```

Remove NA, and calculate proportion
```{r eval = TRUE, echo = TRUE}
thisData <- de %>% 
  select(Country) %>% 
  drop_na()

thisTable <- tabyl(thisData$Country)
names(thisTable)[1] <- 'Country'
#names(thisTable)[3] <- 'proportion'

thisTable <- thisTable[order(-thisTable$n),]
rownames(thisTable) <- c()
formattable(thisTable, align='l')
```

### Type of data

Count frequency in raw data
```{r}
table(de$`Type of data`, useNA = 'always')
```

Remove NA, and calculate proportion
```{r eval = TRUE, echo = TRUE}
thisData <- de %>% 
  select(`Type of data`) %>% 
  drop_na()

thisTable <- tabyl(thisData$`Type of data`)
names(thisTable)[1] <- 'Type_of_data'
#names(thisTable)[3] <- 'proportion'

thisTable <- thisTable[order(-thisTable$n),]
rownames(thisTable) <- c()
formattable(thisTable, align='l')
```

### Study design

Count frequency in raw data
```{r}
table(de$`Study design`, useNA = 'always')
```

Remove NA, and calculate proportion
```{r eval = TRUE, echo = TRUE}
thisData <- de %>% 
  select(`Study design`) %>% 
  drop_na()

thisTable <- tabyl(thisData$`Study design`)
names(thisTable)[1] <- 'Study_design'

thisTable <- thisTable[order(-thisTable$n),]
rownames(thisTable) <- c()
formattable(thisTable, align='l')
studyDesignTable <- thisTable
```

