---
title: "Blue communities"
output: html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(readxl)
library(janitor)
```

### Data from archive of original gsheet
```{r eval = TRUE}
extract_xls <- "data/DATA EXTRACTION FINAL.xlsx"
de <- read_excel(extract_xls, sheet = "Summary DE")
```

### Biosphere reserve

Count frequency in raw data
```{r}
table(de$`Biosphere reserve`, useNA = 'always')
```

Remove NA, fix names and tidy values
```{r}
thisData <- de %>% 
  select('Biosphere reserve') %>% 
  drop_na()

names(thisData) <- 'Biosphere_reserve'
thisData[thisData == 'Komodo MPA',] <- 'Komodo'
thisData[thisData == 'Cat Tien (Dong Nai)',] <- 'Cat Tien'
```

Calculate proportion with frequency
```{r eval = TRUE, echo = TRUE}
thisTable <- tabyl(thisData$Biosphere_reserve)
names(thisTable)[1] <- 'Biosphere_reserve'
names(thisTable)[3] <- 'proportion'
thisTable <- thisTable[order(-thisTable$n),]
thisTable
```

### Country

Count frequency in raw data
```{r}
table(de$Country, useNA = 'always')
```

Remove NA, fix names and tidy values
```{r}
thisData <- de %>% 
  select(Country) %>% 
  drop_na()
```

Calculate frequency and proportion
```{r eval = TRUE, echo = TRUE}
thisTable <- tabyl(thisData$Country)
names(thisTable)[1] <- 'Country'
names(thisTable)[3] <- 'proportion'
thisTable <- thisTable[order(-thisTable$n),]
thisTable
```

### Type of data

Count frequency in raw data
```{r}
table(de$`Type of data`, useNA = 'always')
```

Remove NA, fix names, calculate frequency and proportion
```{r eval = TRUE, echo = TRUE}
thisData <- de %>% 
  select(`Type of data`) %>% 
  drop_na()

thisTable <- tabyl(thisData$`Type of data`)
names(thisTable)[1] <- 'Type_of_data'
names(thisTable)[3] <- 'proportion'
thisTable <- thisTable[order(-thisTable$n),]
thisTable
```

### Study design

Count frequency in raw data
```{r}
table(de$`Study design`, useNA = 'always')
```

Remove NA, fix names and tidy values
```{r}
thisData <- de %>% 
  select(`Study design`) %>% 
  drop_na()
```

Calculate frequency and proportion
```{r eval = TRUE, echo = TRUE}
thisTable <- tabyl(thisData$`Study design`)
names(thisTable)[1] <- 'Study_design'
names(thisTable)[3] <- 'proportion'
thisTable <- thisTable[order(-thisTable$n),]
thisTable
```

