---
title: "Horizontally stacked barcharts"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(readxl)
library(janitor)
library(RColorBrewer)
library(svglite)
```

### Get data
```{r eval = TRUE}
original_xls <- "data/DATA EXTRACTION FINAL (15).xlsx"
de <- read_excel(original_xls, sheet = "Summary DE", .name_repair = "minimal")
Table_1_xls <- "data/Tables for report (21).xlsx"
t1 <- read_excel(Table_1_xls, sheet = "Table 1 final")
```


```{r}
labelonly <-  theme(
  axis.title.x=element_blank(),
  axis.title.y=element_blank(),
  axis.text.x=element_blank(),
  axis.text.y=element_blank(),
  axis.ticks.x=element_blank(),
  axis.ticks.y=element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank()
)
```

```{r}
library(scales)
GreyLong <- colorRampPalette(brewer.pal(9, 'Greys'))(12)
lowGreys2 <- GreyLong[3:4]
#show_col(lowGreys2)
GreenLong <- colorRampPalette(brewer.pal(9, 'Greens'))(12)
lowGreens2 <- GreenLong[5:6]
#show_col(lowGreens2)
OrangeLong <- colorRampPalette(brewer.pal(9, 'Oranges'))(14)
midOranges2 <- OrangeLong[5:6]
#show_col(midOranges2)
RedLong <- colorRampPalette(brewer.pal(9, 'Reds'))(15)
# midReds4 <- RedLong[4:8]
midReds4 <- c("#FCC5AF", "#FCAF93", "#FC9168", "#FB6A4A")
show_col(midReds4)
PurpleLong <- colorRampPalette(brewer.pal(9, 'Purples'))(16)
midPurples4 <- PurpleLong[5:8]
#show_col(midPurples4)
```

```{r}
thisData <- de %>% 
  select(`Study design`) %>% 
  drop_na()

thisTable <- tabyl(thisData$`Study design`)
names(thisTable)[1] <- 'Study_design'

thisTable <- thisTable[order(-thisTable$n),]
rownames(thisTable) <- c()
formattable(thisTable, align='l')
studyDesignTableDE <- thisTable
```

```{r}
# get from Table 1 to see difference
thisData <- t1 %>% 
  select(`Study design`) %>% 
  drop_na()

thisTable <- tabyl(thisData$`Study design`)
names(thisTable)[1] <- 'Study_design'

thisTable <- thisTable[order(-thisTable$n),]
rownames(thisTable) <- c()
studyDesignTableT1 <- thisTable

formattable(studyDesignTableT1, align='l')
```

# OK table 1 lacks rows which messes up the results.
# what's needed is DE unique by author

allRows <- de %>% 
  select(`Author-date`, `Study design`)

names(allRows)[1] <- 'Author'
names(allRows)[2] <- 'Study_design'

# if NA in all 3 columns, remove row
authorBlanks <- allRows[rowSums(is.na(allRows)) != ncol(allRows), ]

authorMulti <- authorBlanks %>%
  fill(Author)

# uniqueness test using Author column
thisData <- unique(authorMulti) 

thisTable <- tabyl(thisData$Study_design)

names(thisTable)[1] <- 'Study_design'

# want Non-comparative first so don't order by n
#thisTable <- thisTable[order(-thisTable$n),]

col_order <- c('Non-comparative', 'CI', 'BA', 'BACI')

orderedTable <- thisTable %>% 
  slice(match(col_order, Study_design))

formattable(orderedTable, align='l')
studyDesignTableT1 <- orderedTable

```{r}
thisTable <- studyDesignTableT1
Name <- thisTable$Study_design
Value <- thisTable$percent
Absolute <- thisTable$n
# percent <- format(round(Value * 100, 0), nsmall = 0)
percent <- (round(Value * 100, digits=0))
Str <- paste0(Absolute, ' (', percent, '%)')

# calculate interval position
df <-  data.frame(Name, Absolute, Value, Str) %>%
  mutate(Name = factor(Name, levels = Name),
         Pos = cumsum(lag(Value, default = 0)) + Value/2) 
studyDesign_df <- df
studyDesign_df
```

# easier to plot outside markdown
df <- studyDesign_df
thisPlot <- ggplot(data = df, aes(x = Pos, y = 0.2, 
                        width = Value, fill = Name)) +
  geom_col(position = "identity", show.legend = FALSE) +
  geom_text(aes(label = Name),
            position = position_fill(vjust = 0.13), size = 5) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.08), size = 5) +
  labelonly +
  scale_fill_manual(values = lowReds4)

#replot with smaller vertical labels
thisPlot <- ggplot(data = df, aes(x = Pos, y = 0.2, 
                        width = Value, fill = Name)) +
  geom_col(position = "identity", show.legend = FALSE) +
  geom_text(aes(label = Name),
            position = position_fill(vjust = 0.13), size = 5) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.08), size = 5) +
  labelonly +
  scale_fill_manual(values = lowReds4)
  
thisPlot

# ggsave(file="svg/studyDesign_horizontal_raw.svg", plot=thisPlot)
ggsave(file="png/table1_studyDesign_horizontal_raw.png", plot=thisPlot)

designHorizontalPlot <- thisPlot  


```{r}
library(magick)
#tmp1 <- image_read('png/studyDesign_horizontal_raw.png')
tmp1 <- image_read('png/table1_studyDesign_horizontal_raw.png')
tmp2 <- image_trim(tmp1)
#image_write(tmp2, path='png/studyDesign_horizontal.png', format='png')
image_write(tmp2, path='png/table1_studyDesign_horizontal.png', format='png')
studyDesign_img <- tmp2
image_info(tmp1)
image_info(tmp2)
```

## Type of data
```{r eval = TRUE, echo = TRUE}
thisData <- de %>% 
  select(`Type of data`) %>% 
  drop_na()

thisTable <- tabyl(thisData$`Type of data`)
names(thisTable)[1] <- 'Type_of_data'

thisTable <- thisTable[order(-thisTable$n),]
rownames(thisTable) <- c()
formattable(thisTable, align='l')
typeOfDataTable <- thisTable
```

```{r}
thisTable <- typeOfDataTable
Name <- thisTable$Type_of_data
Value <- thisTable$percent
Absolute <- thisTable$n
percent <- (round(Value * 100, digits=0))
Str <- paste0(Absolute, ' (', percent, '%)')

# calculate interval position
df <-  data.frame(Name, Absolute, Value, Str) %>%
  mutate(Name = factor(Name, levels = Name),
         Pos = cumsum(lag(Value, default = 0)) + Value/2) 
TypeOfData <- df
TypeOfData
```

```{r}
df <- TypeOfData
thisPlot <- ggplot(data = df, aes(x = Pos, y = 0.2, 
                        width = Value, fill = Name)) +
  geom_col(position = "identity", show.legend = FALSE) +
  geom_text(aes(label = Name),
            position = position_fill(vjust = 0.13), size = 5) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.08), size = 5) +
  labelonly +
  scale_fill_manual(values = lowGreens2)

# ggsave(file="svg/typeOfData_horizontal_raw.svg", plot=thisPlot, width=10, height=8)
ggsave(file="svg/typeOfData_horizontal_raw.svg", plot=thisPlot)
ggsave(file="bitmap/typeOfData_horizontal_raw.png", plot=thisPlot)

typeHorizontalPlot <- thisPlot  
typeHorizontalPlot
```

```{r}
library(magick)
tmp1 <- image_read('bitmap/typeOfData_horizontal_raw.png')
tmp2 <- image_trim(tmp1)
image_write(tmp2, path='bitmap/typeOfData_horizontal.png', format='png')
typeOfData_img <- tmp2
image_info(tmp1)
image_info(tmp2)
```

## Data source
```{r eval = TRUE, echo = TRUE}
sourceData <- de %>% 
  select(`Data source`) %>% 
  drop_na()

thisData <- sourceData  # to save changing common code

thisData[thisData == 'Conference abstract',] <- 'Conf. Abstract'
thisData[thisData == 'Peer-reviewed published literature',] <- 'Peer-reviewed'

thisTable <- tabyl(thisData$`Data source`)
names(thisTable)[1] <- 'Data_source'

# thisTable <- thisTable[order(-thisTable$n),]  # order by Frequency

# Awkward long label on narrow slice will need arrow to external label
#  so move it to end of bar to give option of placing label at side.

orderSource <- c('Peer-reviewed', 'Book', 'Thesis', 'Conf. Abstract')
thisTable <- thisTable %>% 
  slice(match(orderSource, Data_source))

# rownames(thisTable) <- c()  
# another table display package was showing row numbers?
formattable(thisTable, align='l')

dataSourceTable <- thisTable  # preserve for inspection
```

```{r}
thisTable <- dataSourceTable
Name <- thisTable$Data_source
Value <- thisTable$percent
Absolute <- thisTable$n
Str <- paste0(Name, ' (', Absolute, ')')
vLab <- c(0, 1, 1, 0)
percent <- format(round(Value * 100, 0), nsmall = 0)

# calculate interval position
df <-  data.frame(Name, Absolute, Value, Str, vLab) %>%
  mutate(Name = factor(Name, levels = Name),
         Pos = cumsum(lag(Value, default = 0)) + Value/2) 
dataSource <- df
dataSource
```

# deep sideways version
df <- dataSource
thisPlot <- ggplot(data = df, aes(x = Pos, y = 0.22, 
                        width = Value, fill = Name)) +
  geom_col(position = "identity", show.legend = FALSE) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.08),
            alpha = ifelse(df$Name == 'Peer-reviewed', 0, 1),
            size = 4, angle = 90, hjust = 0.35) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.11),
            alpha = ifelse(df$Name == 'Peer-reviewed', 1, 0),
            size = 5, hjust = 0.35) +
  labelonly +
  scale_fill_manual(values = midPurples4)
thisPlot
dataSourceHorizontalDeep <- thisPlot
ggsave(file="png/dataSource_horizontal_deep_raw.png", plot=thisPlot)

```{r}
df <- dataSource
thisPlot <- ggplot(data = df, aes(x = Pos, y = 0.2, 
                        width = Value, fill = Name)) +
  geom_col(position = "identity", show.legend = FALSE) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.08),
            alpha = ifelse(df$Name == 'Peer-reviewed', 0, 1),
            size = 4, angle = 90, hjust = 0.35) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.11),
            alpha = ifelse(df$Name == 'Peer-reviewed', 1, 0),
            size = 5, hjust = 0.35) +
  labelonly +
  scale_fill_manual(values = midPurples4)
thisPlot

```

```{r}
df <- dataSource
# alpha = ifelse(df$Name == 'Peer-reviewed' | df$Name == 'Conf. Abstract', 0, 1),

thisPlot <- ggplot(data = df, aes(x = Pos, y = 0.2, 
                        width = Value, fill = Name)) +
  geom_col(position = "identity", show.legend = FALSE) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.08),
            alpha = ifelse(vLab == 1, 1, 0),
            size = 4, angle = 90, hjust = 0.35) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.07),
            alpha = ifelse(df$Name == 'Peer-reviewed', 1, 0),
            size = 5, hjust = 0.35) +
  geom_text(data = subset(df, Name == 'Conf. Abstract'), 
            label = 'Conf. Abstract (1)',
            size = 4, hjust = 0.2, vjust = -0.2) +
  labelonly +
  scale_fill_manual(values = midPurples4)

# ggsave(file="eps/dataSource_horizontal_raw.eps", plot=thisPlot)
ggsave(file="png/dataSource_horizontal_overflow_raw.png", plot=thisPlot)

dataSourceHorizontalPlot <- thisPlot  
dataSourceHorizontalPlot
```

thisPlot <- ggplot(data = df, aes(x = Pos, y = 0.15, 
                width = Value, fill = Name)) +
  geom_col(position = "identity", show.legend = FALSE) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.06),
            alpha = ifelse(vLab == 1, 1, 0),
            size = 4, angle = 90, hjust = 0.35) +
  geom_text(aes(label = Str),
            position = position_fill(vjust = 0.08),
            alpha = ifelse(df$Name == 'Peer-reviewed', 1, 0),
            size = 5, hjust = 0.35) +
  geom_text(data = subset(df, Name == 'Conf. Abstract'), 
            label = 'Conf. Abstract (1)',
            size = 4, hjust = 0.9, vjust = 9.5) +
  geom_segment(x = 0.96, y = -0.01, 
            xend = 0.96, yend = 0.05, 
            arrow = arrow(length = unit(0.3, 'cm'))) +
  labelonly +
  scale_fill_manual(values = midPurples4)
thisPlot
ggsave(file="png/dataSource_horizontal_arrow_raw.png", plot=thisPlot)

```{r}
library(magick)
#tmp1 <- image_read('bitmap/dataSource_horizontal_raw.png')
tmp1 <- image_read('png/dataSource_horizontal_arrow_raw.png')
#tmp1 <- image_read('png/dataSource_horizontal_deep_raw.png')
tmp2 <- image_trim(tmp1)
#image_write(tmp2, path='png/dataSource_horizontal_deep.png', format='png')
image_write(tmp2, path='png/dataSource_horizontal_arrow.png', format='png')
dataSource_img <- tmp2
image_info(tmp1)
image_info(tmp2)
```
