---
title: "Counting intervention & outcome combinations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(janitor)
library(ztable)
```

```{r echo=FALSE}
extract_xls <- "data/DATA EXTRACTION FINAL (14).xlsx"
DE <- read_excel(extract_xls, sheet = "Summary DE", .name_repair = "minimal")
```

Extract columns for author-date, intervention and outcome.

Reductionist sum found by counting rows unique across all 3 columns.

```{r}
inOutNA <- DE %>% 
  select('Author-date', 'Intervention category', 'Outcome category')
colnames(inOutNA) <- c('Author', 'Intervention', 'Outcome')

# if NA in all 3 columns, remove row
inOut <- inOutNA[rowSums(is.na(inOutNA)) != ncol(inOutNA), ]
inOut
```

Within each column copy previous value down to fill the NA values.

Reduce by only keeping unique rows, dropping any multiples from an author.

```{r}
inOut <- inOut %>%
  fill(Author) %>% 
  fill(Intervention) %>% 
  fill(Outcome)

inOut <- inOut %>% 
  mutate(Intervention = replace(Intervention, Intervention=='Resource Use Management', 'Resource use management'))

reductionist <- unique(inOut) # uniqueness test includes Author column
reductionist
```
  
The mixed intervention "CBNRM and Health intervention" comes from D'Agnes. It may be a problem for matrix chart.

## Numbers for matrix (reductionist version)

```{r}
Freqs <- table(reductionist$Intervention, reductionist$Outcome) 
options(ztable.type="html")
z <- ztable(Freqs) 
# print(z,caption="Intervention and Outcome matrix")
```

```{r}
t1 <- reductionist %>% 
  tabyl(Intervention, Outcome) 
t1
```

There are 5 distinct intervention categories, plus the hybrid "CBNRM and Health intervention".
```{r}
t1[1]
```

There are 7 outcome categories.

```{r}
colnames(t1)[2:length(t1)]
```

